### 2016-02-13 paper/3-features.tex
Add begin/end lookahead mention.

We will not make a detailed comparison with PythonPDEVS here, but only mention some supported features.
Dxex supports, similarly to PythonPDEVS, the following features: direct connection~\cite{SymbolicFlattening}, \textsf{Dynamic Structure DEVS}~\cite{DSDEVS}, termination conditions, and a modular tracing and scheduling framework~\cite{PythonPDEVS}.
But whereas PythonPDEVS only supports optimistic synchronization, dxex support multiple synchronization protocols (though only in parallel).
This is in line with the design principle of PythonPDEVS: allow users to pass performance hints to the simulation kernel.
In our case, a user can pass the simulation kernel sets the synchronization protocol to be used for this model.
Our implementation in C++11 also allows for optimizations which were plainly impossible in an interpreted language.

@@

Always defining a lookahead function might seem redundant, especially if users will never use conservative synchronization.
Especially since defining the lookahead is often non-trivial and dependent on intricate model details.
The more attractive option is for the simulation tool to provide a default lookahead function, such that simulation can run anyway, but maybe not at peak performance.
%Depending on the model, simulation performance might still be faster than sequential simulation.

>>>>

We will not make a detailed comparison with PythonPDEVS here, but only mention some supported features.
Dxex supports, similarly to PythonPDEVS, the following features: direct connection~\cite{SymbolicFlattening}, \textsf{Dynamic Structure DEVS}~\cite{DSDEVS}, termination conditions, and a modular tracing and scheduling framework~\cite{PythonPDEVS}.
But whereas PythonPDEVS only supports optimistic synchronization, dxex support multiple synchronization protocols (though only in parallel).
This is in line with the design principle of PythonPDEVS: allow users to pass performance hints to the simulation kernel.
In our case, a user can pass the simulation kernel the synchronization protocol to be used for this model.
Our implementation in C++11 also allows for optimizations which were plainly impossible in an interpreted language.

@@

Always defining a lookahead function might seem redundant, especially if users will never use conservative synchronization.
Especially since defining the lookahead is often non-trivial and dependent on intricate model details.
The more attractive option is for the simulation tool to provide a default lookahead function, such that simulation can run anyway, but maybe not at peak performance.
Depending on the model, simulation performance might still be faster than sequential simulation.
